Emulating Comparative Oncology Trials with Real-world Evidence Studies (ENCORE): Process Development and Methodological Considerations for Oncology Real-World Data

### 2025-07-06 manuscript/manuscript.qmd
corrected year according to updated reference

Randomized controlled trials (RCTs) are the evidentiary gold standard methodology for establishing the efficacy and safety of medical products. Guided by the 21^st^ Century Cures Act,[@RWEFDA] the Food and Drug Administration (FDA) established a framework to factor considerations for use of real-world evidence (RWE) generated from real-world data (RWD) such as electronic health records (EHR) to support approval of new indications or satisfy postmarketing requirements.[@RWEFDA] Accounting for approximately 30% of new FDA drug approvals, oncology was the disease area with the most new approvals in 2024[@mullard20242023] as well as several indication expansions, and has many areas of high unmet medical need to treat serious conditions. Therefore, RWE can have a particularly important potential to complement evidence from RCTs in the field of oncology. Potential uses include the assessment of effectiveness in specific patient populations that are not adequately represented in RCTs, or the precision oncology-focused discovery of biomarkers among pan-tumor populations that harbor specific genomic and immuno-pathological signatures.

>>>>

Randomized controlled trials (RCTs) are the evidentiary gold standard methodology for establishing the efficacy and safety of medical products. Guided by the 21^st^ Century Cures Act,[@RWEFDA] the Food and Drug Administration (FDA) established a framework to factor considerations for use of real-world evidence (RWE) generated from real-world data (RWD) such as electronic health records (EHR) to support approval of new indications or satisfy postmarketing requirements.[@RWEFDA] Accounting for approximately 30% of new FDA drug approvals, oncology was the disease area with the most new approvals in 2023[@mullard20242023] as well as several indication expansions, and has many areas of high unmet medical need to treat serious conditions. Therefore, RWE can have a particularly important potential to complement evidence from RCTs in the field of oncology. Potential uses include the assessment of effectiveness in specific patient populations that are not adequately represented in RCTs, or the precision oncology-focused discovery of biomarkers among pan-tumor populations that harbor specific genomic and immuno-pathological signatures.
